---
title: "Lab 0 - Hello R!"
author: "Maya Markus-Malone"
date: "1/17/23"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(datasauRus)
```

## Exercise 1

13 rows, 1 column

## Exercise 2

R=-.0645

## Exercise 3

This is the code to plot the data

```{r}
circle_data <- datasaurus_dozen |>
     filter(dataset == "circle")
 ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
     geom_point()
```

Code to get the coefficient

```{r}
 circle_data |>
     summarize(r = cor(x, y))
```

The circle graph R = -.0683. This is very similar to the R from the dino graph.

## Exercise 4

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)

## Exercise 5

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)
